Temporal Variations In Vapor Intrusion Induced Indoor Air Contaminant Concentrations

### 2019-03-21 tex/main.tex
So many things

\begin{table}[htb!]
  \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
  \begin{tabular}{l c c c}
    \toprule
    \textbf{Percentile} & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
    EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995} & 0.16-0.2 & 0.35-0.49 & 1.21-1.49 \\
    ASU house\cite{holton_temporal_2013,guo_identification_2015} & 0.25 & 0.5 & 1.15 \\
    Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34 & 0.74 & 1.27 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[htb!]
  \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
  \begin{tabular}{l c c c}
    \toprule
    \textbf{Percentile} & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
    EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995} & 0.16-0.2 & 0.35-0.49 & 1.21-1.49 \\
    ASU house\cite{holton_temporal_2013,guo_identification_2015} & 0.21 & 0.43 & 0.78 \\
    Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34 & 0.74 & 1.27 \\
    \bottomrule
  \end{tabular}
\end{table}
